---
title: "Taxonomy richness computing with R"
author: "Evans Ehouman"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Taxonomy richness computing with R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
  
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
library(dplyr)
set.seed(1014)
```

# TaxoRich

The `TaxoRich` package can be used to calculate taxon richness from floristic survey.


## Loading `TaxoRich` package

```{r setup}
library(TaxaRich)
```


##`TaxoRich` package functions

 * The `nbfam()` function calculates the sum of all the species from a given family.

 * The `nbgr()` function calculates the sum of all species from  a genera.

 * The `nblfm()` function calculates the sum of all species from  a given life form.

 * The `nbchl()` function calculates the sum of all species from  a given chorological origin.

## References

## Add your tricks
Please contact Evans (ehoumanevans@gmail.com) if you would like to add here a code that may be useful for users (code authorship will be respected).
